Note for Scattering Amplitude Computation

### 2025-04-26 Note/Note.tex
New

@@

\end{tikzpicture}
\end{center}
For the four point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
configuration. There are two feynman diagrams contributing to the color-ordered amplitude.\\
\begin{figure}[htbp]
    \centering
    \includegraphics{4pt.eps}
    \caption{4pt.}
    \label{1}
\end{figure}

For the first diagram, the residue equals to
\begin{equation*}
    \mathcal{R}es|_{s_{12}=0}=\frac{[3 I ] [23]}{[I2]}\times \frac{\avg{I4}\avg{41}}{\avg{1I}}=\frac{\avg{24}[31]\avg{41}[23]}{[42]\avg{24}}
\end{equation*}
Similarly, the second one is
\begin{equation*}
    \mathcal{R}es|_{s_{13}=0}=\frac{\avg{4I}\avg{24}}{\avg{I2}}\times \frac{[31] [I3]}{[1I]}=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23]}
\end{equation*}

@@

We can freely choose $r_1=r_2=1$ or 2, then $\avg{r_1 2}$,$\avg{r_2 1}$,$\avg{r_1 1}$,$\avg{r_2 2}$, two of them equal to 0, so we can conclude that
    A[1,2,3^+,4^+]=0
\subsection{5-point case}
For the 5-point case, we can utilize the BCFW recursion relation which can help us generate higher point amplitude from lower point on-shell subamplitudes. Here, 
we always consider the MHV (Maximal helicity violation) amplitude. 
If there is no special case, we always choose the following BCFW shift
    \sket{\hat{2}}=\sket{2}-z\sket{3},\qquad \qquad \aket{\hat{3}}=\aket{3}+z\aket{3}\\
    \aket{\hat{2}}=\aket{2}, \qquad \sket{\hat{3}}=\sket{3}
where 2 always refers to antiscalar and 3 refers to gauge boson with + helicity.

>>>>

    If there is no special case, we always choose the following BCFW shift
        \begin{gather*}
            \sket{\hat{2}}=\sket{2}-z\sket{3},\qquad \qquad \aket{\hat{3}}=\aket{3}+z\aket{3}\\
            \aket{\hat{2}}=\aket{2}, \qquad \sket{\hat{3}}=\sket{3}
        \end{gather*}
    where 2 always refers to antiscalar and 3 refers to gauge boson with + helicity.

@@

\end{tikzpicture}
\end{center}
For the 4-point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
configuration. There are two feynman diagrams contributing to the color-ordered amplitude.\\
\begin{figure}[htbp]
    \centering
    \includegraphics{4pt.eps}
    \caption{4pt.}
    \label{1}
\end{figure}

Because we choose $[2,3\rangle$ shift here, so there is only one valid BCFW channel
\begin{align*}
    A[1,2,3_1^+,4_2^-]&=\frac{\mdavg{\hat{2}4}{4\hat{I}}}{\avg{\hat{I}\hat{2}}}\times\frac{1}{s_{24}}\times\frac{[\hat{I}\hat{3}][\hat{3}1]}{[1\hat{I}]}\\
    &=\frac{[13][23]}{[14][24]}
\end{align*}
it seems that this amplitude is different from others before, because it is expressed solely in terms of angle brackets, but of course it can be rewritten to another form.
\begin{align*}
    \frac{[13][23]}{[14][24]}&=\frac{\cbrak{23}{31}}{\cbrak{23}{41}}\times \frac{\acbrak{23}{31}}{\acbrak{24}{31}}\\
    &=-\frac{\cbrak{24}{\bcancel{41}}}{\avg{23}\bcancel{[41]}}\times(-1)\frac{\bcancel{[24]}\avg{41}}{\bcancel{[24]}\avg{31}}\\
    &=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
\end{align*}
Also, we can compute it from direct gluing. For the first diagram, the residue equals to
\begin{equation*}
    \mathrm{Res}|_{s_{12}=0}=\frac{[3 I ] [23]}{[I2]}\times \frac{\avg{I4}\avg{41}}{\avg{1I}}=\frac{\avg{24}[31]\avg{41}[23]}{[42]\avg{24}}
\end{equation*}
Similarly, the second one is
\begin{equation*}
    \mathrm{Res}|_{s_{13}=0}=\frac{\avg{4I}\avg{24}}{\avg{I2}}\times \frac{[31] [I3]}{[1I]}=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23]}
\end{equation*}

@@

We can freely choose $r_1=r_2=1$ or 2, then $\avg{r_1 2}$,$\avg{r_2 1}$,$\avg{r_1 1}$,$\avg{r_2 2}$, two of them equal to 0, so we can conclude that
\begin{equation*}
    A[1,2,3^+,4^+]=0
\end{equation*}
\subsection{5-point case}
For the 5-point case, we can utilize the BCFW recursion relation which can help us generate higher point amplitude from lower point on-shell subamplitudes. Here, 
we always consider the MHV (Maximal helicity violation) amplitude.
